### 2016-11-01 ms/ms.tex
Marilia did some editing on the ms

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a long-term data set comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions. High species
  and interaction turnover was ubiquitous across assembling and
  non-assembling communities, though unique interactions turned over
  at higher rates in assembling hedgerows as the networks continually
  reorganized. Nestedness of assembling networks also increased
  through time, but there was no increase in robustness to simulated
  plant extinctions. The sensitivity of networks to cascading
  perturbations, however, increased as the communities assembled, at
  least partially due to accumulating species richness. We elucidate
  some of the mechanisms underlying plant-pollinator network assembly
  and restoration, while providing further evidence that hedgerows are
  a valuable tool for promoting species conservation and ecosystem
  service? provision in agricultural areas.
\end{abstract}

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., in prep). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations can have negative consequences
for the species in the network such as the decrease in abundance of a
plant or pollinator. For example, a pollinator could decrease in
abundance, and the pollination services it provided to the plants it
visited would be diminished. The effected plants would set less seeds,
and decrease in abundance the subsequent year. The pollinators that
depended on those plant species would suffer, and the cascade would
continue to propagate throughout the network. A perturbation could
have a positive effect, like the increase in abundance of a
species. Similar to the negative perturbation, the impact of the
positive perturbation would cascade through the network. The examples
of negative perturbations (e.g., resource collapse, disease,
parasites), however, outnumber possible positive perturbations. Both
of these metrics of network resilience are static --- they do not
account for the ability of species to alter their interaction
depending on circumstances.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would expect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of monitoring
the assembly process or the drought, is not possible. Interestingly,
most assembling hedgerows did not undergo a significant interaction
reorganization immediately after a hedgerow was planted (i.e., the
transition from weedy field margin to hedgerow). This result is
consistent with the finding that in our study system, hedgerow
restoration takes several years to have an impact on the
plant-pollinator communities, and with the observation that hedgerows
do not begin to produce many flowers until $3$--$5$ years following
planting (Kremen and M'Gonigle, in prep).

>>>>

\begin{abstract}  
  The ability of communities to maintain function in the face of
  species extinction is related to the structure of
  networks. Understanding network structure and how it relates to
  network assembly, therefore, is a priority for conservation
  biology. Using a long-term data set comprising nearly $20,000$
  pollinator visitation records, we explore the assembly of
  plant-pollinator communities at native plant restorations in the
  Central Valley of California. Across years, species are highly
  dynamic in their network position, causing community assembly to be
  punctuated by major interaction reorganizations. In contrast, the
  non-assembling networks did not restructure as frequently. Across
  all communities, pollinator species were opportunistic in the
  flowers they visited. The most persistent and generalized species
  were also the most variable in their network positions, contrary to what is expected through prefereantial attachment theory. High species
  and interaction turnover was ubiquitous across assembling and
  non-assembling communities, though unique interactions turned over
  at higher rates in assembling hedgerows as the networks continually
  reorganized. Nestedness of assembling networks also increased
  through time, but there was no increase in robustness to simulated
  plant extinctions. The sensitivity of networks to cascading
  perturbations, however, increased as the communities assembled, at
  least partially due to accumulating species richness. We elucidate
  some of the mechanisms underlying plant-pollinator network assembly
  and restoration, while providing further evidence that hedgerows are
  a valuable tool for promoting species conservation and ecosystem
  service? provision in agricultural areas.
\end{abstract}

@@

We also explored how the robustness to cascading perturbations changed
as the community assembled, using algebraic connectivity --- the
second smallest eigenvalue of the Laplacian matrix
\citep{fiedler1973algebraic} --- as a proxy for network robustness
(Gaiarsa et al., in prep). Algebraic connectivity relates to how
difficult it is to turn a network into completely disconnected groups
of species \citep{costa2007characterization, gibert2013spatial}. The
larger the algebraic connectivity, the more sensitive a network is to
cascading perturbations. Perturbations, such as the decrease in abundance of a
plant or pollinator, can have negative consequences
for the species in the network. For example, pollination service provided to planst could decrease following a decrease in
abundance of a pollinator. The affected plants would set less seeds,
and decrease in abundance the subsequent year. Consequently, other pollinators that
depended on those plant species would also be affected, and the effects of this perturbation would
continue to propagate throughout the network, potentially affecting all species in the community. Alternatively, perturbations could
also have a positive effect. For example, the increase in abundance of a
plant species would lead to an increase in resource availability for the pollinators. The examples
of negative perturbations (e.g., resource collapse, disease spreading,
parasites), however, outnumber possible positive perturbations. It is important to point out that both robustness and algebraic connectivity assume that the network is static --- these metrics do not
account for the ability of species to alter their interaction
depending on circumstances and the resource availability.

@@

We show that the temporal assembly of plant-pollinator networks
following restoration is a highly dynamic process where interactions
often undergo significant reorganizations, the so called changing
points. If these network reorganizations were a product of
environmental forces alone, we would expect to observe the same
changing points at the same periods, consistently across all
sites. However, network changing points in non-assembling communities
are less frequent, and there are few consistent trends in when change
points occurred across all sites. Several sites had network changing
points between years 2009 and 2011 (Fig.~\ref{fig:changePoints}). In
California, 2011 marked the beginning of a multi-year drought. The
assembling hedgerows were not sampled in 2010, so disentangling
whether the changing points are due to skipping a year of monitoring
the assembly process or the drought is not possible. Interestingly,
most assembling hedgerows did not undergo a significant interaction
reorganization immediately after a hedgerow was planted (i.e., the
transition from weedy field margin to hedgerow). This result is
consistent with the finding that in our study system, hedgerow
restoration takes several years to have an impact on the
plant-pollinator communities, and with the observation that hedgerows
do not begin to produce many flowers until $3$--$5$ years following
planting (Kremen and M'Gonigle, in prep).
